Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2014-12-20 wearables_survey.tex
rough intro done.

\section{Introduction}
Basically a longer version of the abstract, plus some additional motivational things thrown in here.

2014 is year of wearables \cite{Forbes}. A survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables \cite{Neilsen} says that most popular devices (61\%), followed by smart watches (45\%) and mHealth (mobile health) devices (17\%). It is estimated that ~15\% use it in daily life \cite{Nilsen}\cite{WearableStatNews}.

End this section with an explicit list of contributions made by this paper.

>>>>

\section{Introduction}
Basically a longer version of the abstract, plus some additional motivational things thrown in here. I feel like I should have a couple sentences which lead into what I am going to talk about, or at least lead in with something catchy and strong. Hmm. Think about what to put here.

A huge paragraph or two on why wearables are important and how much they are in use. Basically, prove that the study is worth doing in the first place. Some sources to use: 2014 is year of wearables \cite{Forbes}. A survey consisting of 3,956 respondents who are either current users or non-users with high interest in wearables \cite{Neilsen} says that most popular devices (61\%), followed by smart watches (45\%) and mHealth (mobile health) devices (17\%). It is estimated that ~15\% use it in daily life \cite{Nilsen}\cite{WearableStatNews}.

People are getting upset and scared about the things that can happen with wearble devices. There was a scandal with fitbit where the 1) profiles were default public and 2) sex counted as an exercise (cite that), how google had to disable facial recognition for glass (cite) along with using voice commands rather than other commands for bystanders to be informed of what is going on (cite). We suspect that there will only be more and more situations like this to come, as wearables get increasingly powerful (cite) and are getting adopted by more people (cite), and across other demographics (cite).

End this section with an explicit list of contributions made by this paper. \\[-.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item we got people's perception on various new threats for wearable devices, a wide range of threats.
\item we found out what matters in their perception of these things--data type, data recipient, and device type and how much each of those matter. We have a cool regression model for that. 
\item we found out how people's perception of threats change when it is with respect to other people consuming the data, or just the device (data type analysis ranking with appserver only verse everyone else). 
\item we got people's risk and benefit assessment of new technologies and capabilities. Most new capabilities are seen as low risk low benefit, but we suspect it's because people aren't familiar. 
\item we found out what people were, nebulously, most concerned with. Privacy, then security, health, finances, social norms. 
\item we calibrate our work so it's relevant and understandable with smartphone research and risk perception research. We can even say that we extended those areas too, if I want to be bold. 
\end{itemize}
